Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-19 manuscript/manuscript.tex
changed LL values in table

\begin{table}[t!]
\caption{\label{tab:empirical_data}
Performance comparison for the models in~\ref{fig:empirical_trees}. 
All ExpCMs describe the evolution of HA better than the GY94 models, as evaluated by the Akaike information criteria~\citep[$\Delta$AIC,][]{posada2004model}
The mean $\omega$ value from each $K=4$ bins is shown for the models with $\Gamma\omega$ rate variation, otherwise simply the fit, gene-wide $\omega$. 
Each ExpCM has a stringency parameter $>1$.
\skhcomment{GY94+$\Gamma\omega$ has one $\omega$ of 0 because of rounding.}
\skhcomment{check LL values}
} 
     \begin{tabular}{cccccccccc}
        \hline
         Model & {\shortstack{Site-specific\\ stationary state}} & $\Gamma\omega$ & $\Delta$AIC & {\shortstack{Log\\ Likelihood}} & {\shortstack{$\omega$\\ (implied dN/dS)}} & {\shortstack{stringency\\ parameter}}\\ \hline
       	ExpCM + $\Gamma\omega$ (H1+H3 avg) & + & + & 0 & -487510 & 0.19,  0.50,  0.90,  1.86 &  1.70\\
	ExpCM (H1+H3 avg) & + & - &  950 & -492270 & 0.15 & 1.78\\
	ExpCM + $\Gamma\omega$ (H1) & + & + & 1306 & -494040  & 0.13 ,  0.44,  0.91,  2.16 & 1.12\\
	ExpCM + $\Gamma\omega$ (H3) & + & + & 1737 & -49620 & 0.09,  0.33,  0.72,  1.77 & 1.28\\
	ExpCM (H1) & + & - & 2556 & -50030 &  0.13 & 1.22\\
	ExpCM (H3) & + & - &  3197 & -50350 & 0.12 & 1.45\\
	GY94 + $\Gamma\omega$ & - & + & 4719 & -51106 & 0.00,  0.03,  0.08,  0.26 & - \\
	GY94 & - & - & 7625 & -52560  & 0.07 & -\\
      \end{tabular}
\end{table}

>>>>

\begin{table}[t!]
\caption{\label{tab:empirical_data}
Performance comparison for the models in~\ref{fig:empirical_trees}. 
All ExpCMs describe the evolution of HA better than the GY94 models, as evaluated by the Akaike information criteria~\citep[$\Delta$AIC,][]{posada2004model}
The mean $\omega$ value from each $K=4$ bins is shown for the models with $\Gamma\omega$ rate variation, otherwise simply the fit, gene-wide $\omega$. 
Each ExpCM has a stringency parameter $>1$.
\skhcomment{GY94+$\Gamma\omega$ has one $\omega$ of 0 because of rounding.}
\skhcomment{check LL values}
} 
     \begin{tabular}{cccccccccc}
        \hline
         Model & {\shortstack{Site-specific\\ stationary state}} & $\Gamma\omega$ & $\Delta$AIC & {\shortstack{Log\\ Likelihood}} & {\shortstack{$\omega$\\ (implied dN/dS)}} & {\shortstack{stringency\\ parameter}}\\ \hline
       	ExpCM + $\Gamma\omega$ (H1+H3 avg) & + & + & 0 & -48751 & 0.19,  0.50,  0.90,  1.86 &  1.70\\
	ExpCM (H1+H3 avg) & + & - &  950 & -49227 & 0.15 & 1.78\\
	ExpCM + $\Gamma\omega$ (H1) & + & + & 1306 & -49404  & 0.13 ,  0.44,  0.91,  2.16 & 1.12\\
	ExpCM + $\Gamma\omega$ (H3) & + & + & 1737 & -49620 & 0.09,  0.33,  0.72,  1.77 & 1.28\\
	ExpCM (H1) & + & - & 2556 & -50030 &  0.13 & 1.22\\
	ExpCM (H3) & + & - &  3197 & -50350 & 0.12 & 1.45\\
	GY94 + $\Gamma\omega$ & - & + & 4719 & -51106 & 0.00,  0.03,  0.08,  0.26 & - \\
	GY94 & - & - & 7625 & -52560  & 0.07 & -\\
      \end{tabular}
\end{table}
